\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{multicol}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\parindent}{0pt}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom lists
\newcommand{\resumeItem}[1]{\item{#1}}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}

\begin{document}
\fontfamily{ppl}\selectfont % Palatino

% Header
\begin{center}
    {\Huge\textbf{Igor Lucindo Cardoso}}
\end{center}
\vspace{-5mm}

\begin{center}
    \small{
    \href{mailto:Igor.Cardoso@ttu.edu}{Igor.Cardoso@ttu.edu} \,|\, 
    \socialicon{\faGlobe} \href{https://igorlucindo.github.io}{igorlucindo.github.io} \,|\, 
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/igorlucindo/}{igorcardoso} \,|\, 
    \socialicon{\faGithub} \href{https://github.com/igorlucindo}{igorlucindo}
    }
\end{center}

% Summary
\vspace{-5.5mm}
\section{\textbf{Professional Summary}}
\vspace{1mm}
\small{
\begin{itemize}[leftmargin=10pt]
    \item PhD student specializing in Operations Research, Mixed-Integer Programming (MIP), and Graph Theory.
    \vspace{-1mm}
    \item Published author with research focused on GPU-accelerated optimization and decision tree algorithms.
    \vspace{-1mm}
    \item Experienced in developing full-stack optimization tools using Python, CUDA, and Gurobi.
\end{itemize}
}

% Education
\vspace{-5mm}
\section{\textbf{Education}}
\vspace{1mm}

\textbf{Texas Tech University (TTU)} \hspace*{\fill} 2025 – Present \\
Ph.D. in Industrial Engineering \hspace*{\fill} GPA: 4.00/4.00 
\vspace{1.5mm}

\textbf{Getulio Vargas Foundation (FGV)} \hspace*{\fill} 2023 – 2024 \\
M.A. Courses in Mathematical Modeling
\vspace{1.5mm}

\textbf{Military Institute of Engineering (IME)} \hspace*{\fill} 2020 – 2024 \\
B.S. in Electronic Engineering \hspace*{\fill} GPA: 8.25/10.00


% Publications
\vspace{-1.5mm}
\section{\textbf{Publications}}
\vspace{1mm}

\noindent\hangindent=1em\hangafter=1
\textbf{Cardoso, I.}, Teodoro, G., Validi, H. (2026). \textbf{A Polytime and Interpretable Approach for Solving Wordle}. Submitted to \textit{Operations Research}.
\vspace{0.5mm}

\noindent\hangindent=1em\hangafter=1
Gutierrez, R., \textbf{Cardoso, I.}, Validi, H. (2026). \textbf{Sport Scheduling to Minimize Travels at the FIFA World Cup 2026}. Submitted to \textit{Optimization Letters}.
\vspace{0.5mm}

\noindent\hangindent=1em\hangafter=1
\textbf{Cardoso, I.}, et al. (2024). \href{https://ieeexplore.ieee.org/document/10596873}{\textbf{Comparing Pre-Trained Object Detection Models for Autonomous Grasp on Affordable Prosthetic Hands}}. \textit{IEEE MeMeA}.

\vspace{1mm}
\textit{\small{Manuscripts in Progress}}

\noindent\hangindent=1em\hangafter=1
\textbf{Cardoso, Igor} and Validi, Hamidreza.
\textbf{On Solving the Network-Based Portfolio Optimization Problems}.
\textit{Manuscript in preparation}, 2026.


% Research Experience
\vspace{-2mm}
\section{\textbf{Research Experience}}
\vspace{1mm}

\textbf{Research Assistant, Texas Tech University (TTU)} \hspace*{\fill} 2025 – Present
\vspace{-1mm}
\resumeItemListStart
    \resumeItem{Developing novel algorithms for NP-hard combinatorial problems, leveraging GPU acceleration and decomposition techniques to solve large-scale instances.}
    \vspace{-0.5mm}
    \resumeItem{Advisor: Dr. Hamidreza Validi.}
\resumeItemListEnd
\vspace{1mm}

\textbf{Research Experience for Undergraduates, Memorial University (MUN)} \hspace*{\fill} 2023
\vspace{-1mm}
\resumeItemListStart
     \resumeItem{Developed autonomous grasping capabilities for a prosthetic hand by integrating machine learning, computer vision, and predictive modeling to drive system optimization.}
    \vspace{-0.5mm}
    \resumeItem{Advisor: Dr. Vinicius P. da Fonseca.}
\resumeItemListEnd


% Honors & Awards
\vspace{-2mm}
\section{\textbf{Honors \& Awards}}
\vspace{1mm}
\begin{itemize}[leftmargin=10pt, noitemsep] % 'noitemsep' saves space
    \item TTU Tye Industrial Endowment Engineering Scholarship \hspace*{\fill} 2026
    \item INFORMS Student Chapter Annual Award (Cum Laude) \hspace*{\fill} 2025
    \item 1st place, Shell Eco-marathon "The Road to 2050" \hspace*{\fill} 2021
    \item 5th place, Petrobras Challenge (RoboIME) \hspace*{\fill} 2021
    \item Gold Medal, Brazilian Math Olympiad (OBMEP) \hspace*{\fill} 2018
\end{itemize}


% Affiliations
\vspace{-5.5mm}
\section{\textbf{Affiliations \& Activities}}
\vspace{1mm}
\resumeItemListStart
    \resumeItem{\textbf{INFORMS Student Chapter:} Active member engaging in seminars and collaborative research.}
    \resumeItem{\textbf{Journal Club Presenter:} Discussing and analyzing peer-reviewed research in Operations Research.}
    \resumeItem{\textbf{Previous Activities:} Robotics Club (RoboIME), Shell Eco-marathon Team.}
\resumeItemListEnd


% Software & Projects
\vspace{-3mm}
\section{\textbf{Software \& Projects}}
\vspace{0.5mm}

\textbf{Wordle Optimization Solver} \hspace*{\fill} \textit{Python, CUDA, Decision Trees} \\
GPU-accelerated solver achieving a theoretically optimal 3.42 average guesses. \href{https://igorlucindo.github.io/wordle-optimization-GAME/}{\color{darkblue}[View App]}
\vspace{0.5mm}

\textbf{FIFA World Cup 2026 Scheduler} \hspace*{\fill} \textit{Python, JS, MIP Solvers} \\
Interactive web app using MIP to optimize match scheduling and minimize travel. \href{https://igorlucindo.github.io/fifa-world-cup-2026-scheduler-APP/}{\color{darkblue}[View App]}
\vspace{0.5mm}

\textbf{Expense Splitter} \hspace*{\fill} \textit{Python, Linear Programming} \\
Optimization tool to minimize transactions required to settle shared expenses. \href{https://igorlucindo.github.io/expense-splitter-APP/}{\color{darkblue}[View App]}


% Skills
\vspace{-3mm}
\section{\textbf{Skills}}
\begin{tabbing}
    \hspace{4cm} \= \kill
    Programming \> Python, C/C++, Matlab, Julia, Java, JavaScript, HTML, CSS, FPGA, SQL \\
    Tools \> Gurobi, Cuda/GPU, Git, \LaTeX, Linux, NetworkX, ROS, OpenCV, Arduino \\
    Languages \> Portuguese (native), English (fluent), French (intermediate) \\
\end{tabbing}


\end{document}